Determining the alternatives for scalar implicature

### 2016-01-24 Paper/Paper.Rmd
reorg into 1 2 3

We begin by presenting the computational framework we use throughout the paper. We next describe a series of experiments deisgned to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items. These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements. To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgements, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgements with high accuracy.

@@

To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an onine restaurant review (where $m \in \{1, 2, 3, 4, 5\}$). We then use experiments to measure three components of the model. First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiments 1a, 3a, and 4). Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2). Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances.

# Experiment 1: Entailment scales

```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1a,b, 3a,b and 4."}

@@

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1a (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar \`liked.\'"}

@@

Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ (Experiment 1a) and pragmatic judgments $p_{L_1}(m \mid u)$ (Experiment 1b) for five pairs of scalar items taken from @vantiel2014. Scales and alternative utterances are shown in Figure \ref{fig:allScalesTable}. Each pair of scalar items consists of a "weaker" term (e.g. "some") and a stronger term (e.g. "all"). We begin with these classic members of the Horn scale [@horn1972] as a test of the hypothesis that these alternatives are all that is necessary to predict the strength of listeners' pragmatic inferences.

@@

We recruited 30 participants from Amazon Mechanical Turk (AMT) for Experiment 1a; two participants were excluded because they reported having a native language other than English for a final sample of 28 participants. We recruited 50 for Experiment 1b, also from AMT, and data for 7 participants were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.

@@

Figure \ref{fig:stimuli_exp1} shows the experimental setup for both experiments. In Experiment 1a, the literal listener task, participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank. Each participant saw all scalar item and star rating combinations, in a random oder.

In Experiment 1b, the pragmatic listener experiment, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave. Each participant was presented with all scalar items in a random order.

@@

ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("Star Rating") +
  ylab("Proportion Judgments") + 
  scale_colour_solarized() + 
  theme_bw() + 
  theme(legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"))

####################################
# OLD PLOTS -------------------------
# plotData <- speakerE8 %>%
#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
# # Literal listener: Entailment (e8)
# e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
#   geom_line() +
#   ylab("Percent yes") +
#   geom_linerange(aes(ymin = speaker.p - cil, 
#                      ymax = speaker.p + cih)) +
#   ggtitle("Literal semantics")
# 
# # Pragmatic listener: Entailment (e6)
# plotData <- listenerE6 %>%
#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
# e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
#                  aes(x = stars, y = listener.p, fill = degree)) +
#   geom_bar(stat = "identity", position = "dodge") +
#   facet_wrap(~degree) +
#   ylab("Proportion of star-ratings chosen") +
#   ggtitle("Pragmatic judgments") +
#   theme(legend.position="none")
# gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
```

Figure 2 plots literal listener $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4. Data from 1a is (...). We see clear variation in semantic judgments between scalar families in all Experiments. For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved". We will address distributional similarity across the studies in later sections.

```{r}
# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
# subset(speakerE8, degree == "low")$cnt.judgment
# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
#            subset(speakerE8, degree == "low")$cnt.judgment)
```

# Experiment 2: What are the alternatives?

In Experiment 1 we obtained literal semantic compatibility and pragmatic judgments for five pairs of scalar terms. We would like to extend the scale descriptions for each of these pairs to include other plausible alternatives. We chose to take an empirical approach rather than assign alternatives arbitrarily. We adopted a modified cloze task, inspired by Experiment 2 in van Tiel (2014) and asked participants to generate alternatives for us.

@@

Using Amazon's Mechanical Turk, 30 workers were paid $0.20 to participate. All participants were native English speakers and naive to the purpose of the experiment.

### Design and procedure
Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____" with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" and asked to generate three unique alternatives.

## Results and Discussion
Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g.. "good/excellent", "memorable/unforgettable") were similarly long-tailed, however the size and content of the alternate sets were diverse. (SOMETHING MORE MORE FORMAL HERE???)

```{r exp2_altsPlot_likedLoved, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}

# Subset alternatives for demo
plotData <- subset(alternativesData, scale == "liked_loved")
removeRows <- which(plotData$alt == "liked" | plotData$alt == "loved")
plotData <- plotData[-removeRows, ]
# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
altsPlot <- ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
  geom_bar(stat="identity") + ylim(0, 52) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", "liked/loved")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

altsPlot
```

# Experiment 3a,b: Incorporating top alternatives

In Experiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales. In Experiment 2, we asked participants to generate plausible alternatives to these items. In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to include the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2. The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.

@@

Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. Thirty participants were recruited for Experiment 3a (Literal Listener task). Data for six participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 24 participants.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener task). Data for five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.

## Procedure
The procedure of Experiments 3a,b follow the same form as Experiments 1a,b with the expanded set of target scalar items.

@@

Run glmer() here:
```{r}

```
To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject. Results indicate (...)

Run elmer() here:
```{r}

```

To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject. Results indicate.

While conducting our analysis we realized that our literal semantic distributions for each scalar family were roughly split between two negative valenced items and two positively valenced items while neutral alternatives appeared to be excluded. (This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4, we explore the addition of a neutrally valenced scalar alternative for each scalar family.

# Experiment 4: Full scales - adding a neutral alternative
In Experiment 4, we continue to extend the alternative sets, each by one additional scalar item. While we simply took the top two alternatives generated in Experiment 2 for the additional alternatives in Experiments 3a,b, in this case we chose a subjectively "neutral" valenced scalar item from among the alternatives generated in Experiment 2. The idea was to simulate a "full" set of alternatives, with negative, neutral and positive valenced items for each scalar family. The purple colored items in Table 1 denote additional scalar items added in Experiments 4.

## Participants
Thirty participants were recruited on Amazon Mechanical Turk and paid $0.20 for their participation. There were no data exclusions due to training failures or native language requirements, leaving a total sample of thirty participants, all native English speakers, naive to the purpose of the experiment.

## Procedure
The procedure of Experiment 4 follow the same form as Experiments 1a and 3a with the addition of a neutrally valence scalar item.

## Results and Discussion
Distributions for neutrally valenced scalar did appear fairly Gaussian, occupying a literal semantic previously unoccupied by the other alternatives.

Run glmer() here:
```{r}

```
To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject. Results indicate (...)

Run elmer() here:
```{r}

```

To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject. Results indicate.

@@

Using literal semantic data from Experiments 1a, 3a and 4 we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation available to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Experiment 3a. The "Full" model included the full set of alternatives, including a neutral valenced alternative. These data were measured in Experiment 4.

@@

# General Discussion
By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature. Model fit with human judgement was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items. In fact, we found that both neutral and negative valence scalar items contribute to human-like implicature generation within our framework.

>>>>

We begin by presenting the computational framework we use throughout the paper. We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items. These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements. To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgements, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgements with high accuracy.

@@

To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an onine restaurant review (where $m \in \{1, 2, 3, 4, 5\}$). We then use experiments to measure three components of the model. First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiment 1). Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2). Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances (Experiment 3).

# Experiment 1: Literal listener task

```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1, 2, and 3"}

@@

```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \`liked.\'"}

@@

Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014. We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives. The two-alternative entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference. The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}

@@

In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT). In the two-alternative condition, two participants were excluded because they reported having a native language other than English for a final sample of 28 participants. In the four-alternative condition,  six participants were excluded for either failing to pass two training trials a non-English native language, leaving a total sample of 24 participants. In the five-alternative condition, there were no data exclusions due to training failures or native language requirements, leaving a total sample of 30 participants.

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup. Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank. Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.

The two-alternatives condition included only the scalar pairs from @vantiel2014. The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2. The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2.

@@

ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("Star Rating") +
  ylab("Proportion Judgments") + 
  scale_colour_solarized() + 
  theme_bw() + 
  theme(legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"))
```

Figure 2 plots literal listener $p_{L0}(m|u)$ distributions for the three conditions. Several trends are visible. First, in each scale, the alternatives spanned the star scale, such that there were alternatives that were highly compatible with both the lowest and highest numbers of stars. Second, there was clear variability between scalar families. For example, compatibility judgments for the top items in the "memorable / unforgettable" scale were more similar than those for "good / excellent" or "liked / loved." Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.

# Experiment 2: Alternative Elicitation

To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 2 of @vantiel2014.

@@

We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.

Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.

```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}

# Subset alternatives for demo
plotData <- alternativesData %>%
  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
  mutate(prop = n / sum(n))

# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
  geom_bar(stat="identity") + 
  ylim(0, 52) + 
  labs(x = "alternative", y = "counts") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
  ylab("Proportion of responses")
```

Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items "liked" and "loved" (combined). Alternative distributions for the other scalar pairs (e.g.. "good/excellent", "memorable/unforgettable") were similarly long-tailed.

# Experiment 3: Pragmatic Listener

In Experiment 3, we asked participants to make pragmatic listener judgements.

CONDITIONS

@@

We recruited 150 participants from AMT, 50 for each condition. Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants. In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.

## Procedure

Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave. Each participant was presented with all scalar items in a random order. The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.

@@

@@

Using literal semantic data from Experiment 1 we conducted three simulations with our model. Each simulation used the specific literal semantic data to specify the scale representation available to our model. The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014). These data were measured in Experiment 1a. The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2. These data were measured in Experiment 3a. The "Full" model included the full set of alternatives, including a neutral valenced alternative. These data were measured in Experiment 4.

@@

# General Discussion

By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature. Model fit with human judgement was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items. In fact, we found that both neutral and negative valence scalar items contribute to human-like implicature generation within our framework.

### 2016-01-24 Paper/Paper.tex
reorg into 1 2 3

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt a food-review paradigm: we assume that speakers and
listeners are trying to communicate the number of stars in an onine
restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
experiments to measure three components of the model. First, to measure
literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
participants to judge whether a message is applicable to a particular
meaning (Experiments 1a, 3a, and 4). Second, to generate a set of
plausible alternative messages in \(U\), we elicit alternatives directly
(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
ask participants to interpret a speaker's utterances.

\section{Experiment 1a,b: Entailment
scales}\label{experiment-1ab-entailment-scales}

\begin{CodeChunk}
\begin{figure}[t]
\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1a,b, 3a,b and 4]{Stimuli for Experiments 1a,b, 3a,b and 4.}\label{fig:allScalesTable}
\end{figure}
\end{CodeChunk}

@@

\caption[(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L_0}(m \mid u)\) (Experiment 1a) and
pragmatic judgments \(p_{L_1}(m \mid u)\) (Experiment 1b) for five pairs
of scalar items taken from Tiel (2014). Scales and alternative
utterances are shown in Figure \ref{fig:allScalesTable}. Each pair of
scalar items consists of a ``weaker'' term (e.g. ``some'') and a
stronger term (e.g. ``all''). We begin with these classic members of the
Horn scale (Horn, 1972) as a test of the hypothesis that these
alternatives are all that is necessary to predict the strength of
listeners' pragmatic inferences.

@@

Figure \ref{fig:stimuli_exp1} shows the experimental setup for both
experiments. In Experiment 1a, the literal listener task, participants
were presented with a target scalar item and a star rating (1--5 stars)
and asked to judge the compatibility of the scalar item and star-rating.
Compatibility was assessed through a binary ``yes/no'' response to a
question of the form ``Do you think that the person thought the food was
\_\_\_\_?" where a target scalar was presented in the blank. Each
participant saw all scalar item and star rating combinations, in a
random oder.

In Experiment 1b, the pragmatic listener experiment, participants were
presented with a one-sentence prompt containing a target scalar item
such as ``Someone said they thought the food was \_\_\_\_\_.''
Participants were then asked to generate a star rating representing the
rating they thought the reviewer likely gave. Each participant was
presented with all scalar items in a random order.

@@

Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions obtained
in Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
variation in semantic judgments between scalar families in all
Experiments. For example, compatibility judgments for ``memorable'' and
``forgettable'' are more similar than those for ``good / excellent'' or
``liked / loved''. We will address distributional similarity across the
studies in later sections.

\section{Experiment 2: What are the
alternatives?}\label{experiment-2-what-are-the-alternatives}

In Experiment 1 we obtained literal semantic compatibility and pragmatic
judgments for five pairs of scalar terms. We would like to extend the
scale descriptions for each of these pairs to include other plausible
alternatives. We chose to take an empirical approach rather than assign
alternatives arbitrarily. We adopted a modified cloze task, inspired by
Experiment 2 in van Tiel (2014) and asked participants to generate
alternatives for us.

@@

Using Amazon's Mechanical Turk, 30 workers were paid \$0.20 to
participate. All participants were native English speakers and naive to
the purpose of the experiment.

@@

Participants were presented a target scalar term from our original
entailment set embedded in a sentence such as, ``In a recent restaurant
review someone said they thought they the food was \_\_\_\_" with a
target scalar presented in the ``\_\_\_\_." Participants were then asked
to generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_\_?'' and asked to generate three unique
alternatives.

@@

Figure 3 plots the combined counts of alternatives generated for the
scalar items ``liked'' and ``loved.'' Alternative distributions for the
other scalar pairs (e.g.. ``good/excellent'',
``memorable/unforgettable'') were similarly long-tailed, however the
size and content of the alternate sets were diverse. (SOMETHING MORE
MORE FORMAL HERE???)

@@

\caption[Caption goes here]{Caption goes here}\label{fig:exp2_altsPlot_likedLoved}
\end{figure*}
\end{CodeChunk}

\section{Experiment 3a,b: Incorporating top
alternatives}\label{experiment-3ab-incorporating-top-alternatives}

In Experiment 1a,b we measured literal semantics and pragmatic judgments
for Entailment scales. In Experiment 2, we asked participants to
generate plausible alternatives to these items. In Experiments 3a,b we
use the same experimental design for both literal semantics and
pragmatic judgment tasks, however we now expand the set of scalar items
to include the original Entailment pairs from Experiments 1a,b with the
top two alternatives generated for each scalar family by participants in
Experiment 2. The orange colored items in table 1 denote additional
scalar items added in Experiments 3a,b.

@@

Participants for both studies were recruited on Amazon Mechanical Turk
and paid \$0.20 for their participation. Thirty participants were
recruited for Experiment 3a (Literal Listener task). Data for six
participants was thrown out after participants either failed to pass two
training trials or were not native English speakers, leaving a total
sample of 24 participants.

Fifty participants were recruited for Experiment 3b (Pragmatic Listener
task). Data for five participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 45 participants.

@@

The procedure of Experiments 3a,b follow the same form as Experiments
1a,b with the expanded set of target scalar items.

@@

Run glmer() here:

To test whether literal listener compatibility judgments differed
between Experiment 1a and 3a we ran a mixed effects model, regressing
responses to the binary compatibility measure on scale, degree, and
Experiment with random effects by subject. Results indicate (\ldots{})

Run elmer() here:

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Experiment with random effects by subject.
Results indicate.

While conducting our analysis we realized that our literal semantic
distributions for each scalar family were roughly split between two
negative valenced items and two positively valenced items while neutral
alternatives appeared to be excluded. (This pattern was true of all the
scalar families, except for ``some ~all'' in which the top two
alternatives were positive valenced ``most'' and negative valenced
``none''.) In Experiment 4, we explore the addition of a neutrally
valenced scalar alternative for each scalar family.

\section{Experiment 4: Full scales - adding a neutral
alternative}\label{experiment-4-full-scales---adding-a-neutral-alternative}

In Experiment 4, we continue to extend the alternative sets, each by one
additional scalar item. While we simply took the top two alternatives
generated in Experiment 2 for the additional alternatives in Experiments
3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
item from among the alternatives generated in Experiment 2. The idea was
to simulate a ``full'' set of alternatives, with negative, neutral and
positive valenced items for each scalar family. The purple colored items
in Table 1 denote additional scalar items added in Experiments 4.

\subsection{Participants}\label{participants-3}

Thirty participants were recruited on Amazon Mechanical Turk and paid
\$0.20 for their participation. There were no data exclusions due to
training failures or native language requirements, leaving a total
sample of thirty participants, all native English speakers, naive to the
purpose of the experiment.

\subsection{Procedure}\label{procedure-1}

The procedure of Experiment 4 follow the same form as Experiments 1a and
3a with the addition of a neutrally valence scalar item.

\subsection{Results and Discussion}\label{results-and-discussion-3}

Distributions for neutrally valenced scalar did appear fairly Gaussian,
occupying a literal semantic previously unoccupied by the other
alternatives.

Run glmer() here:

To test whether literal listener compatibility judgments differed
between Experiment 1a and 3a we ran a mixed effects model, regressing
responses to the binary compatibility measure on scale, degree, and
Experiment with random effects by subject. Results indicate (\ldots{})

Run elmer() here:

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Experiment with random effects by subject.
Results indicate.

\section{Model Runs}\label{model-runs}

Using literal semantic data from Experiments 1a, 3a and 4 we conducted
three simulations with our model. Each simulation used the specific
literal semantic data to specify the scale representation available to
our model. The ``entailment'' model used only the original pair of
scalar items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``Top two'' model extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Experiment 3a. The ``Full'' model included
the full set of alternatives, including a neutral valenced alternative.
These data were measured in Experiment 4.

>>>>

To instantiate our signaling game with a tractable message set \(M\), in
our studies we adopt a food-review paradigm: we assume that speakers and
listeners are trying to communicate the number of stars in an onine
restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
experiments to measure three components of the model. First, to measure
literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
participants to judge whether a message is applicable to a particular
meaning (Experiment 1). Second, to generate a set of plausible
alternative messages in \(U\), we elicit alternatives directly
(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
ask participants to interpret a speaker's utterances (Experiment 3).

\section{Experiment 1: Literal listener
task}\label{experiment-1-literal-listener-task}

\begin{CodeChunk}
\begin{figure}[t]
\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1, 2, and 3]{Stimuli for Experiments 1, 2, and 3}\label{fig:allScalesTable}
\end{figure}
\end{CodeChunk}

@@

\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
\end{figure*}
\end{CodeChunk}

Experiment 1 was conducted to approximate literal listener semantic
distributions \(p_{L_0}(m \mid u)\) for five pairs of scalar items taken
from Tiel (2014). We include three conditions in Experiment 1,
corresponding to the sets of alternatives within a scale that
participants were presented with: two alternatives (``entailment''),
four alternatives, and five alternatives. The two-alternative entailment
condition makes a test of the hypothesis that the two members of the
classic Horn scale (Horn, 1972) are the only alternatives necessary to
predict the strength of listeners' pragmatic inference. The four- and
five-alternative conditions then add successively more alternatives to
test whether including a larger number of alternatives will increase
model
fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
Participants were presented with a target scalar item and a star rating
(1--5 stars) and asked to judge the compatibility of the scalar item and
star-rating. Compatibility was assessed through a binary ``yes/no''
response to a question of the form ``Do you think that the person
thought the food was \_\_\_\_?" where a target scalar was presented in
the blank. Each participant saw all scalar item and star rating
combinations for their particular condition (see Figure
\ref{fig:allScalesTable}), in a random oder.

The two-alternatives condition included only the scalar pairs from Tiel
(2014). The four-alternatives condition included the two scalar items
plus the top two alternatives generated for each scalar family by
participants in Experiment 2. The five-alternatives condition included
the four previous items plus one more ``neutral'' item chosen from those
alternatives generated in Experiment 2.

@@

Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions for the
three conditions. Several trends are visible. First, in each scale, the
alternatives spanned the star scale, such that there were alternatives
that were highly compatible with both the lowest and highest numbers of
stars. Second, there was clear variability between scalar families. For
example, compatibility judgments for the top items in the ``memorable /
unforgettable'' scale were more similar than those for ``good /
excellent'' or ``liked / loved.'' Finally, there was substantial
consistency in ratings for items that were repeated across experiments,
suggesting that this paradigm elicited stable judgments from
participants.

\section{Experiment 2: Alternative
Elicitation}\label{experiment-2-alternative-elicitation}

To elicit empirical alternatives for the scales we used in Experiment 1,
we adopted a modified cloze task inspired by Experiment 2 of Tiel
(2014).

@@

We recruited 30 workers on AMT. All participants were native English
speakers and naive to the purpose of the experiment.

@@

Participants were presented a target scalar term from our original
entailment set embedded in a sentence such as, ``In a recent restaurant
review someone said they thought they the food was \_\_\_\_," with a
target scalar presented in the ``\_\_\_\_." Participants were then asked
to generate plausible alternatives by responding to the question, ``If
they'd felt differently about the food, what other words could they have
used instead of \_\_\_\_\_?'' They were prompted to generate three
unique alternatives.

@@

\begin{CodeChunk}
\captionsetup{width=0.8\textwidth}\begin{figure}[t]

@@

\caption[Caption goes here]{Caption goes here}\label{fig:exp2_altsPlot_likedLoved}
\end{figure}
\end{CodeChunk}

Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar
items ``liked'' and ``loved'' (combined). Alternative distributions for
the other scalar pairs (e.g.. ``good/excellent'',
``memorable/unforgettable'') were similarly long-tailed.

\section{Experiment 3: Pragmatic
Listener}\label{experiment-3-pragmatic-listener}

In Experiment 3, we asked participants to make pragmatic listener
judgements.

CONDITIONS

@@

We recruited 150 participants from AMT, 50 for each condition. Data for
7 participants in the two-alternative condition were excluded after
participants either failed to pass two training trials or reported a
non-English native language, leaving a total sample of 43 participants.
In the four-alternative condition, data from five participants was
thrown out after participants either failed to pass two training trials
or were not native English speakers, leaving a total sample of 45
participants.

@@

Participants were presented with a one-sentence prompt containing a
target scalar item such as ``Someone said they thought the food was
\_\_\_\_\_.'' Participants were then asked to generate a star rating
representing the rating they thought the reviewer likely gave. Each
participant was presented with all scalar items in a random order. The
experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.

@@

\section{Model Results}\label{model-results}

Using literal semantic data from Experiment 1 we conducted three
simulations with our model. Each simulation used the specific literal
semantic data to specify the scale representation available to our
model. The ``entailment'' model used only the original pair of scalar
items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``Top two'' model extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Experiment 3a. The ``Full'' model included
the full set of alternatives, including a neutral valenced alternative.
These data were measured in Experiment 4.
